Maenpuen *et al.* --American Journal of Botany-- Appendix S1

### 2022-06-20 ms/LMA_method.Rmd
clean main text

```{r tb1, echo=FALSE, eval=FALSE}
tab1 <- read.csv("../data/sma_sp_ld_tab.csv")
colnames(tab1) <- c("Data", "Slope", "Intercept", "*R^2^*")

tab1 <- tab1 |>
  mutate(Data = case_when(
    Data == "Dense~Thick~Large" ~ "Dense-thick-large",
    Data == "Dense~Thick~Small" ~ "Dense-thick-small",
    Data == "Dense~Thin~Large" ~ "Dense-thin-large",
    Data == "Dense~Thin~Small" ~ "Dense-thin-small",
    Data == "Nondense~Thick~Large" ~ "Nondense-thick-large",
    Data == "Nondense~Thick~Small" ~ "Nondense-thick-small",
    Data == "Nondense~Thin~Large" ~ "Nondense-thin-large",
    Data == "Nondense~Thin~Small" ~ "Nondense-thin-small",
    TRUE ~ Data
  ))
if ("html" == knitr::opts_knit$get("rmarkdown.pandoc.to")) {
  tab1 |>
    kable(format = "html") |>
    kable_classic()
} else if ("docx" == knitr::opts_knit$get("rmarkdown.pandoc.to")) {
  tab1 |>
    kable(format = "pipe")
} else if ("latex" == knitr::opts_knit$get("rmarkdown.pandoc.to")) {
  tab1 |>
    kable(format = "pipe")
}
```

@@

**Fig. 3.**
Relationships between petiole to leaf dry mass ratio and (a) leaf area and (b) whole-leaf to leaf disc LMA ratio.
Blue solid lines indicate ordinary least squares (OLS) regressions.
The 95% confidence intervals are presented as the shaded area.
All the correlations are significant (P < 0.001).
All the samples were obtained with a diameter 1.0-cm leaf punch.

>>>>

@@

**Fig. 3.**
Relationships between petiole to leaf dry mass ratio and (a) leaf area and (b) whole-leaf to leaf disc LMA ratio.
Blue solid lines indicate ordinary least squares (OLS) regressions.
The 95% confidence intervals are presented as the shaded area.
All the correlations are significant (P < 0.001).
Note that all the samples were obtained with a diameter 1.0-cm leaf punch.
